---
title: "Book Bans Ban Books?"
subtitle: "Library Usage in Areas Affected by Book Bans"
author: "Emily Chen"
format: html
---

## Introduction

slkfdjdlsfjlskjf

## Background and Hypotheses

**Public Libraries and Book Bans**

-   public libraries targeted

-   why public libraries? book bans are usually in school libraries

**\[Some social theory, look at previous book ban articles\]**

## Methods

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)

hits_combined_df_grouped <- read.csv("hits_combined_df_grouped.csv")

bar_plot <- hits_combined_df_grouped[order(hits_combined_df_grouped$tot_count, decreasing = TRUE), ] %>%
  head(20) %>% 
  ggplot(aes(x = tot_count, y = DMA)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(
    title = "Top 20 Number of\nBans by DMA",
    x = "Count",
    y = "DMA"
  ) +
  theme_minimal() + # Adjust the theme as needed
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels if needed

# Show the plot
print(bar_plot)
```

```{r echo=FALSE}
hits_combined_df <- read.csv("hits_combined_df.csv")

hist(hits_combined_df$avg_hits_next_month - hits_combined_df$avg_hits_prev_month, main = "Distribution of Difference of Library Searches", xlab = "Difference in Average Hits (Next Month - Previous Month)", ylab = "Frequency")

top_10_table <- read.csv("top_10_table.csv") %>%
  select(-X)

knitr::kable(top_10_table, format = "html")
```

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
library(sf)
library(ggplot2)
library(dplyr)

# Read the shapefile
dma_boundary <- st_read("./data/dma_boundary.geojson")
state_boundary <- st_read("./data/us_states.geojson")

# Read the Google Trends analysis data
clean_pen_index <- read.csv("./outputs/clean_pen_index.csv")  # Adjust the file path and format accordingly

map_dma <- clean_pen_index %>%
  select(Month, Year, Trends_DMA, DMA, STATE) %>%
  group_by(Trends_DMA, DMA, STATE) %>%
  summarize(count = n()) %>%
  distinct()

# Extract the last three characters from Trends_DMA
map_dma$dma_code <- as.numeric(substr(map_dma$Trends_DMA, nchar(map_dma$Trends_DMA) - 2, nchar(map_dma$Trends_DMA)))
map_dma$STATE <- gsub(" ", "", map_dma$STATE)

dma_boundary$STATE <- substr(dma_boundary$dma_1, nchar(dma_boundary$dma_1) - 1, nchar(dma_boundary$dma_1))

# Merge the attribute data with the shapefile based on the extracted common column
merged_data <- left_join(dma_boundary, map_dma, by = c("dma0" = "dma_code", "STATE"))

# Plot the merged data
ggplot() +
  geom_sf(data = merged_data, aes(fill = count), color = "white") +  
  # geom_sf(data = state_boundary, color = "grey", fill = NA) +  # Add state boundaries
  theme_void() +  # Removes background axes and grid lines
  theme(plot.title = element_text(hjust = 0.5)) +  # Center the title
  ggtitle("Book Bans and Challenges by DMA from 2021-2023") +
  scale_fill_gradientn(colors = c("blue", "yellow", "red"), na.value = "grey") +
  labs(fill = "Number of Bans\nor Challenges")


```

## Analysis and Results

Hypothesis 1:

Figure 1:

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
# Read the Google Trends analysis data
library_index <- read.csv("outputs/library-index-full.csv")

# Merge the attribute data with the shapefile based on the extracted common column
merged_data <- left_join(dma_boundary, library_index, by = c("dma0" = "code"))

# Plot the merged data
ggplot() +
  geom_sf(data = merged_data, aes(fill = avg_revenue_2021), color = "white") +  
  # geom_sf(data = state_boundary, color = "grey", fill = NA) +  # Add state boundaries
  theme_void() +  # Removes background axes and grid lines
  theme(plot.title = element_text(hjust = 0.5)) +  # Center the title
  ggtitle("Library Revenue by DMA in 2021") +
  scale_fill_gradientn(colors = c("blue", "yellow", "red"), na.value = "grey") +
  labs(fill = "Average Revenue in 2021\n(Dollars)")
```

Table 1:

```{r echo=FALSE, warning=FALSE}
test3 <- read.csv("test.csv")
dma_pop <- read.csv("outputs/dma_pop.csv")
hits_combined_df_grouped <- hits_combined_df_grouped %>%
  left_join(dma_pop, by = "code")

ols_model <- lm(avg_revenue_2021 - avg_revenue_2019 ~ tot_count + tot_pop, data = hits_combined_df_grouped)

# Summarize the model
summary(ols_model)
```

Table 2:

```{r echo=FALSE}
glm_model <- glm(tot_searches_after ~ tot_count + tot_pop, data = hits_combined_df_grouped, family = Gamma)

summary(glm_model)
```

Hypothesis 2:

Table 3:

```{r echo=FALSE}
# Fit OLS model
ols_model <- lm(avg_hits_next_month - avg_hits_prev_month ~ count + num_lib_2021, data = hits_combined_df)

# Summarize the model
summary(ols_model)
```

Figure x:

```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
# Read the Google Trends analysis data
library_index <- read.csv("outputs/library_index.csv")

# Merge the attribute data with the shapefile based on the extracted common column
merged_data <- left_join(dma_boundary, library_index, by = c("dma0" = "code"))

# Plot the merged data
ggplot() +
  geom_sf(data = merged_data, aes(fill = std_avg_index), color = "white") +  
  # geom_sf(data = state_boundary, color = "grey", fill = NA) +  # Add state boundaries
  theme_void() +  # Removes background axes and grid lines
  theme(plot.title = element_text(hjust = 0.5)) +  # Center the title
  ggtitle("Library Usage Index by DMA in 2021") +
  scale_fill_gradientn(colors = c("blue", "yellow", "red"), na.value = "grey") +
  labs(fill = "Average Library\nUsage Index")
```

Table 4:

```{r echo=FALSE}
# Fit OLS model
ols_model <- lm(std_avg_index_2021 - std_avg_index_2019 ~ tot_count + tot_pop, data = hits_combined_df_grouped)

# Summarize the model
summary(ols_model)
```

Table 5:

```{r echo=FALSE}
# Fit OLS model
ols_model <- lm(std_avg_index_2021 ~ tot_count + tot_pop, data = hits_combined_df_grouped)

# Summarize the model
summary(ols_model)
```

## Discussion

## Conclusion & Limitations

## Bibliography
